The Morality of Arbitrage

### 2017-05-23 Draft/draft2.Rmd
Update to draft2.Rmd

>>>>

In the nomenclature of finance a Dutch book is an arbitrage and the person making a Dutch book against an opponent is called an arbitrageur. For de Finetti the bookmaker whose gain is certain in a given bet is no different than the trader who earns a guaranteed profit by buying low and selling high when an asset is mispriced.

For de Finetti probabilities are prices. In modern finance theory prices are probabilities. In the end it is an equivalence.

Once seen through the lens of subjective probability, it becomes clear that what applies to mispriced assets also applies to misplaced probabilities. They are both examples of incoherent beliefs.
